---
title: "MTHS3003 Portfolio 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

## Instructions

1. Enter your student number in place of `12345678` in the **R** block below:
```{r} 
Student_Number=20497614
```

Student Number: `r Student_Number`

2. Load in the data sets **Car_Sales_Z.csv** and **Car_Battery_Z.csv** with Z replaced by the last number in your student number.
```{r}
# Load in data sets: Use read.csv
car_sales_data<-read.csv("Car_Sales_4.csv")
car_battery_data<-read.csv("Car_Battery_4.csv")
library(fitdistrplus)

```

Do not change the Mark or Feedback Comments.

### Data Set 1 

a. 

```{r}
sales<-car_sales_data$x
summary(sales)

print("quartile summary")
print(quantile(sales))
print(paste("standard deviation for the sale is ", sd(sales), "hence there is no much variance in the sales of car"))
print(paste("The data is left skewed and half of the data lies between median and upper quartile region. 25% of data lies between upper whiskers and lower quartile region and the other 25% of data lies between lower quartile and median, Whereas, between median and upper quartile region half of the data were present"))


```
```{r}
boxplot(sales, horizontal=TRUE,xlab="sales of car")
```

**Mark (out of 4):** `r m1=NA`  
**Feedback Comment:**  

b. 

```{r}
no_of_cars_sold<-length(sales)
no_of_brand_1_cars_sold<-sum(sales==1, na.rm=TRUE)
prob_brand_1_sales = no_of_brand_1_cars_sold/no_of_cars_sold
print(paste("probability of 1 car sold in a given weeks is ",prob_brand_1_sales))

```

**Mark (out of 2):** `r m2=NA`  
**Feedback Comment:**  

c. 

```{r}
start<-1
end<-8
count = 0;
while(end <= 52){
  count = count+1
  start = start + 1
  end = end + 1
}
mean_8_weeks<-rep(NA, count)
variance_8_weeks<-rep(NA, count)

start<-1
end<-8
i<-1
while(end <= 52){
  mean_8_weeks[i]<-mean(sales[start:end])
  variance_8_weeks[i]<-var(sales[start:end])
  start = start + 1
  end = end + 1
  i = i + 1
}
mean_avg_8_weeks<-median(mean_8_weeks)
variance_avg_8_weeks<-median(variance_8_weeks)
print(paste("value of mean for cars sold in period of 8 weeks is ", mean_avg_8_weeks))
print(paste("value of variance for cars sold in period of 8 weeks is ", variance_avg_8_weeks))
```



**Mark (out of 2):** `r m3=NA`  
**Feedback Comment:**  

d. 

```{r}
probability_per_week_0<-sum(sales==0)/no_of_cars_sold
prob_cdf_23weeks<-dbinom(23, size = no_of_cars_sold, prob = probability_per_week_0)
print(paste("probability that there will be 23 weeks in 2023 where 0 Brand X cars will be sold is", prob_cdf_23weeks))
```

**Mark (out of 2):** `r m4=NA`  
**Feedback Comment:**  

### Data Set 2 

a. 

```{r}
batteryA_lifetime = car_battery_data$lifetime[car_battery_data$type=='A']
batteryB_lifetime = car_battery_data$lifetime[car_battery_data$type=='B']
print("Distribution for both lifetime of battery A and B are right skewed. The data were distributed ")
print(paste("mean of lifetime of battery A is ", mean(batteryA_lifetime)))
print(paste("mean of lifetime of battery B is ", mean(batteryB_lifetime)))
print(paste("the mean lifetime of battery of B is slightly greater than battery A"))
print(paste("standard deviation of battery A is", sd(batteryA_lifetime)))
print(paste("standard deviation of battery B is", sd(batteryB_lifetime)))
print(paste("The data of battery A lifetime is dispersed more when compared to battery B lifetime"))
print(paste("lifetime range of battery A min :", min(batteryA_lifetime), " max : ", max(batteryA_lifetime)))
print(paste("lifetime range of battery B min :", min(batteryB_lifetime), " max : ", max(batteryB_lifetime)))
print("the range of Battery A is higher when compared to range of Battery B lifetime")
```

```{r}
hist(batteryA_lifetime, freq = FALSE, xlab = "Battery A lifetime", main = "Battery A")
```

```{r}
hist(batteryB_lifetime, freq = FALSE, xlab = "Battery B lifetime", main = "Battery B")
```

**Mark (out of 4):** `r m5=NA`  
**Feedback Comment:**  
```{r}
y<-fitdist(batteryB_lifetime, distr = "gamma", method = "mle")
print(y)
```

b. 

```{r}


mean_battery_b<-mean(batteryB_lifetime)
standard_deviation<-sd(batteryB_lifetime)
# shape and rate values were found using fitdist method shown in the above cell
shape<-5.3384562
rate<-0.1183597
print("The gamma distribution fits the data")
print(paste("shape of the gamma distribution", shape))
print(paste("rate of the gamma distribution", rate))
print(paste("the mean of the curve is ", mean(batteryB_lifetime)))
print(paste("the standard deviation of the curve is ", sd(batteryB_lifetime)))


```
```{r}
hist(batteryB_lifetime, freq = FALSE)
curve(dgamma(x, shape ,rate), 0, 250, col=2, add=TRUE)
```

**Mark (out of 4):** `r m6=NA`  
**Feedback Comment:**


c. 

```{r}

p <-0.03

values = seq(15, 17, by = 1)
month<-0
for (value in values){
  if(round(pgamma(value, shape, rate), 2) == p){
    month<-value
  }
}

 print(paste("batteries are replaced for free if the battery life is less than or equal to ", round(qgamma(0.03, shape, rate),2), " months")) 
```

**Mark (out of 2):** `r m7=NA`  
**Feedback Comment:**

**Total Mark (out of 20):** `r m1+m2+m3+m4+m5+m6+m7`  
**Feedback Comment:**
