---
title: "MTHS3003 Portfolio 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

## Instructions

1. Enter your student number in place of `12345678` in the **R** block below:
```{r} 
Student_Number=20497614
```

Student Number: `r Student_Number`

2. Load in the data sets **Drug_New_Z.csv** and **Drug_A_Z.csv** with Z replaced by the **fifth** number in your student number.
```{r}
# Load in data sets: Use read.csv
drug_data<-read.csv("Drug_new_7.csv")
drug_a<-read.csv("Drug_A_7.csv")
```

Do not change the Mark or Feedback Comments.

### Data Set 1 

a. 

```{r}
print(table(drug_data))
```

**Mark (out of 2):** `r m1=NA`  
**Feedback Comment:**  

b. 

```{r}
N<-length(drug_data$Response)
N_X<-sum(drug_data$Drug=='X')
N_X_Y<-sum(drug_data$Drug=='X'&drug_data$Response=='Yes')
prob_Y_X<-N_X_Y/N_X
print(paste("the probability of yes when given drug X is : ",prob_Y_X))
```

**Mark (out of 2):** `r m2=NA`  
**Feedback Comment:**  

c. 

```{r}
No_total<-sum(drug_data$Response=='No')
A_total<-sum(drug_data$Drug=='A')
Exp_A_No<-(A_total * No_total)/N
print(paste("the expected number of no response for drug A is : ",Exp_A_No))
```

**Mark (out of 3):** `r m3=NA`  
**Feedback Comment:**  

d. 

```{r}
chi_test<-chisq.test(drug_data$Drug, drug_data$Response, correct=FALSE)
print(paste("probability value", chi_test$p.value))
#pchisq(q=1.523948, df=2, lower.tail=FALSE)
if(chi_test$p.value < 0.05){
  print("we reject the null hypothesis that there is independence between drug and improvement in health")
}else{
  print("we accept the null hypothesis that there is independence between drug and improvement in health")
}
```


**Mark (out of 3):** `r m4=NA`  
**Feedback Comment:**  

### Data Set 2 

a. 

```{r}
after<-drug_a$after
before<-drug_a$before
plot(before, after, xlab = "before drug", ylab = "after drug", main="well being score")
```

**Mark (out of 1):** `r m5=NA`  
**Feedback Comment:**  

b. 

```{r}
model_drug<-lm(after~before)
alpha<-model_drug$coef[1]
beta<-model_drug$coef[2]
print(paste("alpha : ", alpha))
print(paste("Beta : ", beta))
```

**Mark (out of 2):** `r m6=NA`  
**Feedback Comment:**  

c. 

```{r}
plot(before, after, xlab = "before drug", ylab = "after drug")
abline(a=alpha, b=beta)
```

**Mark (out of 1):** `r m7=NA`  
**Feedback Comment:**  

d. 

```{r}
hist(model_drug$residuals, main="well being score before and after drug A",xlab="Residuals",freq=FALSE) # Plot 
curve(dnorm(x,0,summary(model_drug)$sigma),-10,10,lty=2,add=TRUE)
plot(model_drug$fitted.values,model_drug$residuals,xlab="Fitted values",ylab="Residuals",main="well being score before and after drug A")
abline(h=0,lty=2)
print(paste("the residual values are normally distributed and size of residual not depend on the value of fitted value hence it is a reasonable linear model  "))
```

**Mark (out of 3):** `r m8=NA`  
**Feedback Comment:**  

e. 

```{r}
pred<-predict(model_drug, newdata = drug_data[1:57,],interval="prediction")
plot(before, after, xlab = "before drug", ylab = "after drug")
lines(before[1:57],pred[,1],lty=1)
lines(before[1:57],pred[,2], lty=2)
lines(before[1:57],pred[,3], lty=2)

before_wellbeing<-50
confidence_interval<-predict(model_drug, newdata=data.frame(before=before_wellbeing), interval="prediction") 
print("95% confidence interval")
print(paste("lower bound : ", confidence_interval[2], " upper bound : ", confidence_interval[3]))
print(paste("predicted value after drug is ", confidence_interval[1]))
```

**Mark (out of 3):** `r m9=NA`  
**Feedback Comment:**


**Total Mark (out of 20):** `r m1+m2+m3+m4+m5+m6+m7+m8+m9`  
**Feedback Comment:**