---
title: "MTHS3003 Portfolio 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

## Instructions

1. Enter your student number in place of `12345678` in the **R** block below:
```{r} 
Student_Number=20497614
```

Student Number: `r Student_Number`

2. Load in the data sets **Bottle_New_Z.csv** and **Bottle_Check_Z.csv** with Z replaced by the **sixth** number in your student number.
```{r}
# Load in data sets: Use read.csv
data<-read.csv("Bottle_New_6.csv")
data2<-read.csv("Bottle_Check_6.csv")
```

Do not change the Mark or Feedback Comments.

### Data Set 1 

a. 

```{r}
new_bottle<-data$x
mean_bottle<-mean(new_bottle)
variance_bottle<-var(new_bottle)
print(paste("mean :", mean_bottle))
print(paste("variance :", variance_bottle))
```

**Mark (out of 2):** `r m1=NA`  
**Feedback Comment:**  

b. 

```{r}
alpha <-0.05
t_test_value<-t.test(new_bottle)
print(paste("95% confidence interval is [", t_test_value$conf.int[1], " , ", t_test_value$conf.int[2],"]"))
print(paste("mean :", mean_bottle))
```

**Mark (out of 3):** `r m2=NA`  
**Feedback Comment:**  

c. 

```{r}
significance_level = 0.1
ans<-t.test(new_bottle, mu=750, alternative ="greater", conf.level = 0.90)
print("the wine bottle should contain 750ml of wine. Hence the wine filled above that level were considered to be overfilled")
p_value<-ans$p.value
print(paste("The probability value is ", p_value))
print(paste("confidence interval is [", ans$conf.int[1], " , ", ans$conf.int[2],"]"))
if(p_value < significance_level){
  print("The hypothesis is rejected because probability value less than significance value")
}else{
  print("The hypothesis is accepted because probability value greater than significance value")
}
```

**Mark (out of 4):** `r m3=NA`  
**Feedback Comment:**  

### Data Set 2 

a. 
```{r}
s_d<-2.1
pAA<-rep(NA, 14)
sample_size<-10
mu<-750
for(i in 1:14){
  machineRow<-data2[[paste("Machine.",i, sep = "")]]
  sample_mean<-mean(machineRow)
  standard_dev_mean<-s_d/sqrt(sample_size)
  z_score<-abs((sample_mean - mu)/standard_dev_mean)
  pAA[i]<-2*pnorm(q=z_score, lower.tail = FALSE)
  print(paste("Probability values for machine", i, " :", pAA[i]))
}


```



**Mark (out of 6):** `r m4=NA`  
**Feedback Comment:**  

b. 

```{r}
N<-14
alpha<-0.04
plot(sort(pAA), xlab = "machines", ylab = "probability value")
lines(1:N,alpha*(1:N)/N,col=2)
```
```{r}
N<-14
sorted_p<-sort(pAA)
q_value<-rep(NA, N)
dit<-c()
for(i in 1 : N){
  q_value[i]<-(i/N)*alpha
  if(sorted_p[i] < q_value[i]){
    dit<-append(dit, sorted_p[i])
  }
}
print("hypothesis rejected machines")
for(i in 1 : N){
  if(is.element(pAA[i], dit)){
    print(paste("machine", i))
  }
}


```



**Mark (out of 5):** `r m5=NA`  
**Feedback Comment:**  

**Total Mark (out of 20):** `r m1+m2+m3+m4+m5`  
**Feedback Comment:**